\documentclass[a4paper,11pt]{article}

% Packages for formatting and encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.5cm,top=1.5cm,right=1.5cm,bottom=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

% Link configuration
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Resume - Jahat Trinidad},
}

% Section formatting
\titleformat{\section}
{\Large\bfseries\uppercase}
{}
{0em}
{}[\titlerule]

\titlespacing{\section}{0pt}{10pt}{6pt}

% Command for experience/project entries
\newcommand{\entryItem}[4]{
    \noindent \textbf{#1} \hfill \textbf{#2} \\
    \textit{#3} \hfill \textit{#4}
}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Jahat Jassiel Trinidad Leon}} \\ [0.25cm]
    Lima, Peru \\[0.1cm]
    \href{mailto:jahatjassiel@outlook.com}{jahatjassiel@outlook.com} | +51 912 506 265 | \href{https://linkedin.com/in/trinitybytes}{linkedin.com/in/trinitybytes}
\end{center}

% --- PROFILE ---
\section{Professional Profile}
Software Engineering student specialized in \textbf{C++}, \textbf{Full Stack development} and \textbf{databases}. Experience leading teams of up to 6 people using Scrum and GitFlow. Developed 12+ projects: from CLI applications with advanced data structures (AVL, graphs, heap) to web platforms with React and TypeScript. Seeking an internship to apply my skills in C++, SQL and web development.

% --- EDUCATION ---
\section{Education}
\noindent \textbf{Universidad Peruana de Ciencias Aplicadas (UPC)} \hfill Lima, Peru \\
\textit{Software Engineering} \hfill 2024 -- Present (Expected graduation: 2028) \\
\textbf{Key Courses:} Algorithms and Data Structures, Database Design, Web Development, Software Patterns.

% --- TECHNICAL SKILLS ---
\section{Technical Skills}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Languages:} C++17/STL (Advanced), TypeScript, JavaScript ES6+, SQL, HTML5, CSS3.
    \item \textbf{Frontend \& Backend:} React, Node.js, Tailwind CSS, Bootstrap 5, Cytoscape.js.
    \item \textbf{Databases:} SQL Server, MongoDB. Triggers, stored procedures, relational modeling.
    \item \textbf{Algorithms \& DS:} AVL, Hash, Heaps, Graphs. TSP, Dijkstra, topological sorting.
    \item \textbf{DevOps \& Tools:} Git, GitHub, GitFlow, GitHub Actions (CI/CD), Figma, Linux.
    \item \textbf{Languages:} Spanish (Native), English (B1), Portuguese (A2).
\end{itemize}

% --- FEATURED PROJECTS ---
\section{Featured Projects}

\entryItem{CourseraClone - Educational Platform in C++}{}{Product Owner \& Lead Dev (Team of 3)}{2024-2025}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Complete LMS in \textbf{C++17}: users, courses, payments and QR certificates. \textbf{12+ data structures} (AVL, Hash, Graphs).
    \item MVC architecture, RAII, JSON persistence. Web microservices with \textbf{React + TypeScript + Node.js}.
\end{itemize}

\entryItem{Mink'a - Circular Economy Platform}{}{Project Lead (Team of 6)}{2025}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Led end-to-end web development with \textbf{Scrum} (6 sprints, \textbf{140+ commits}, 6 releases).
    \item UX/UI design in Figma, complete \textbf{GitFlow}, CI/CD with GitHub Actions, GitHub Pages deployment.
\end{itemize}

\noindent\textit{More projects: GreenCircuit (TSP), CurriculumFLOW, ForestHero2 $\rightarrow$ \href{https://github.com/trinity-bytes}{github.com/trinity-bytes}}

% --- PROFESSIONAL EXPERIENCE ---
\section{Experience}

\entryItem{Asociacion Educativa Adventista Sur Oriental del Peru}{Madre de Dios}{Computer Science Teacher}{Mar -- Dec 2023}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Taught basic web programming and digital tools to high school students.
\end{itemize}

\entryItem{Subgerencia de Seguridad Ciudadana - MPO}{Oxapampa}{Surveillance Monitor \& Community Manager}{Aug 2022 -- Feb 2023}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Managed institutional social media and video surveillance systems monitoring.
\end{itemize}

% --- VOLUNTEERING ---
\section{Volunteering}
\noindent \textbf{Municipalidad Provincial de Oxapampa} \hfill 2023 \\
\textit{Youth Environmental Promoter (100 Hours)}

\end{document}
